\section{Notation and Problem Statement}~\label{sec:notation}

A \textit{transition system} for bit-level hardware
modelling is a 3-tuple $T = \langle I,V,\delta \rangle$, where $V = \{v_1,\dots ,v_n\}$
is a finite set of \textit{state variables} ranging over the Booleans.
The propositional formula $I[V]$ over the variables in 
$V$ specifies the \textit{initial states} of the system. 
Corresponding to the variables in $V$ is a set of primed \textit{next-state} variables $V' = \{v_1', \dots, v_n'\}$.
The formula $\delta[V,V']$ represents the system's \textit{transition relation}; it specifies the relationship that the system realizes between current and next states at each discrete step of operation.

A \textit{state} $s$ of $T$ is an assignment of Boolean values to the variables in $V$.
If $F[V]$ is a formula over the variables $V$, we write $F(s)$ to say that $s$ makes the formula true.
So, for example, the initial states of a system are all the states $s$ for which $I(s)$. Similarly, if $R[V,V']$ is a relation over the variables $V$ and $V'$, we write $R(s_1,s_2)$ to say that the states $s_1$ and $s_2$ jointly satisfy this relation. Here, $s_2$ will, of course, be an assignment of values to the variables in $V'$. In general, when we mention a state $s$
it will be clear from contexts the underlying set of variables $s$ that assigns Boolean values to.

In the verification methods we investigate, it is common to analyse sequences of state transitions chained together.
We introduce sets of state variables $V_0, \dots, V_k$, where $V_0$ encode the initial state of the system and $V_i$, encode the state reached after $i>0$ transitions. With this machinery, the formula

\[ \bigwedge_{i{=}0}^{k{-}1}\delta[V_i, V_{i+1}]\] 

\noindent characterizes $k$ steps of the transition system.
We call a sequence of states $s_j,\dots,s_k$ a~\textit{trace}
if $\delta(s_i,s_{i{+}1})$ for $i=j,\dots,k{-}1$.  A trace is
said to be \textit{initialized} if $I(s_j)$.
  
A \textit{safety property} $P[V]$ is a predicate over the variables $V$ of $T$.  We will
say a state $s$ is \textit{good} with respect to this property if $P(s)$. Otherwise it is \textit{bad}.
A property $Q$ is an \textit{inductive invariant} for a safety propety $P$ if $Q$ implies $P$, every initial state satisfies $Q$, and $Q[V] \wedge \delta[V,V']$ implies $Q[V']$.

\subsection{Problem Statement} 

We now define the \textit{safety verification} of a transition system~$T = \langle I,V,\delta\rangle$.
This is commonly known as the \textit{hardware model checking problem}.  
Given a safety property $P$, the problem is to decide whether, starting from any initial state, a bad state can be reached following any sequence of transitions allowed by the transition relation. In other words, is there an initialized trace of the system whose final state is bad? One way to confirm that every such final is good is to exhibit an inductive invariant that implies $P$.

