% ---------------------------------------------------------------------
% Journal article on the hardware property checking via software netlists.
%
%   - 14 pages maximum, including everything
%   - TCAD requires 30% new content.
%   - page charges apply
% ---------------------------------------------------------------------

% For final copy to IEEE
\documentclass[journal]{IEEEtran}

% For the initial submission
%\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}

% ---------------------------------------------------------------------
% External packages - keep these minimal!
% ---------------------------------------------------------------------
\usepackage{graphicx}
\usepackage{import}
\usepackage{times}
\usepackage{microtype}
\usepackage{array}
\usepackage{graphicx,wrapfig}
\usepackage{cite}
\usepackage{tikz}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{multirow}
\usetikzlibrary{plotmarks}
\usepackage{pgfplotstable}
\usepackage{pgfplots}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{stmaryrd}
%\usepackage{mathptm}
\usepackage{color}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{comment}
\usepackage{psfrag}
\usepackage{epsfig}
\usepackage{wasysym} 
%\usepackage{subfigure}
\usepackage{paralist}
\usepackage[algo2e,linesnumbered,ruled,lined]{algorithm2e}
\usepackage{hyperref}
\usepackage[subnum]{cases}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{dcolumn}
\newcolumntype{Y}{D..{5.2}}
\newcolumntype{R}{D..{2.2}}
\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
\makeatother

\newcommand{\tool}[1]{\textsc{#1}\xspace}
\newcommand{\cbmcv}{\tool{cbmc 5.0}}
\newcommand{\symex}{\tool{path-symex}}
\newcommand{\ebmc}{\tool{ebmc}}
\newcommand{\hector}{\tool{hector}}
\newcommand{\slec}{\tool{slec}}
\newcommand{\symexv}{\tool{path-symex 5.0}}
\newcommand{\ebmcv}{\tool{ebmc 4.2}}
\newcommand{\hwcbmcv}{\tool{hw-cbmc 5.0}}
\newcommand{\verifox}{\tool{verifox 0.5}}
\newcommand{\acdcl}{\tool{acdcl}}
\newcommand{\summarizer}{\tool{summarizer 1.0}}
%\newcommand{\v{2}c}{\tool{v2c 0.4}}
\newcommand{\ABC}{\tool{ABC}}
\newcommand{\yosys}{\tool{Yosys 0.5}}
\newcommand{\longversion}[1]{}

\newcommand{\Remote}[1]{}
%\newcommand{\mydef}[1]{\begin{definition}#1\end{definition}}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
 

\newcommand{\rmcmt}[1]{{\color{magenta}{#1}}}%#1

\lstdefinestyle{base}{
  language=C,
  emptylines=1,
  breaklines=true,
  escapeinside={(*}{*)},
  basicstyle=\ttfamily\color{black},
  moredelim=**[is][\color{magenta}]{~}{~},
  %moredelim=**[is][\color{red}]{@}{@},
  moredelim=**[is][\color{blue}]{'}{'}
}


% Use millimetres as unit of length, of course.
% ---------------------------------------------------------------------
\setlength{\unitlength}{1mm}

% ---------------------------------------------------------------------
% Any macros we define will ultimately go here. Only absolutely 
% essential macros to be used!
% ---------------------------------------------------------------------
\input{symbols}

% ---------------------------------------------------------------------
% Start of document
% ---------------------------------------------------------------------
\begin{document}

% ---------------------------------------------------------------------
% Title, authors, abstract, keywords
% ---------------------------------------------------------------------
%\title{Moving beyond Bits and Words to Software for Formal Hardware Property Verification}
\title{Comparison of Precise and Abstraction-based tools for RTL verification} 

\author{Rajdeep Mukherjee, 
        Peter Schrammel,
        Daniel Kroening, 
        Tom Melham, \\
        Antoine M{\'i}ne,
        Michael Tautschnig and
        Eugene Goldberg
        \thanks{R. Mukherjee, D. Kroening and T. Melham are at 
                University of Oxford, Department of Computer Science,
                Wolfson Building, Parks Road,
                Oxford, OX1 3QD, England.}
        \thanks{P. Schrammel is at School of Informatics, University of Sussex, 
                Chichester 2 2R302, Sussex, UK}
        \thanks{E. Goldberg is at Diffblue Limited, Oxford, UK}
        \thanks{M. Tautschnig is at 
                School of Electronic Engineering and Computer Science,
                Queen Mary University of London
                Mile End Road, London E1 4NS, UK}
        \thanks{A. M{\'i}ne is at Engineering School, UPMC University, Paris}}
\markboth{IEEE Transactions on Computer-Aided Design of Integrated
          Circuits And Systems, Vol. XX, No. Y, Month 2004}%
         {Mukherjee et al.: Hardware Propety Verification using Software Analyzers}

% Create the title
\maketitle
% \IEEEpeerreviewmaketitle

\begin{abstract}
Folk wisdom in formal hardware verification community is to synthesize a 
hardware design into bit-level netlist.  This technique uses propositional satisfiability 
solvers (SAT) to reason about the correctness of bit-blasted verification 
conditions generated from the netlist representation using a bounded or unbounded 
verification algorithm.  However, most bit-level verification algorithms heavily 
relies on the SAT solvers to generate invariants or finding counterexamples. 
%
An alternative approach is to synthesize a design into word-level netlist which 
is then solved using a Satisfiability Modulo Theory (SMT) solver.  However, 
word-level verification flow has not seen much adoption in commercial EDA tools 
due to the performance bottleneck of word-level SMT solvers.  The tight coupling 
between the verification algorithm and SAT/SMT solvers often limits the scalability 
of these tools.   
%


In this paper, we present a novel formal verification flow that synthesize a 
Register Transfer Level (RTL) design into a software like representation and 
expressed in ANSI-C. We call this \emph{software netlist}. 
The software netlist representation allows us to leverage various software verification 
technologies inlcuding abstract interpretation techniques which was never applied to 
RTL verification.  
%

	
This paper experimentally evaluates formal RTL verification by 
synthesizing the RTL design into two different netlist representations -- 
\emph{bit-level netlist} and \emph{software netlist}.  The bit-level 
netlist is expressed in AIGER format, whereas the software 
netlist is expressed in C language. 
%and is an \emph{exact} representation of the RTL design. 
%
Conventional tools for RTL verification typically reason over 
the bit-level netlist by translating it to a CNF formula following 
Tseitin transformation.  
%   
On the other hand, the software netlist representation allows us 
to leverage various software verification technologies 
inlcuding abstract interpretation techniques which was never 
applied to RTL verification. 
% 
To this end, we present an emperical evaluation of various unbounded formal 
verification algorithms such as Predicate Abstraction, $k$-induction, 
Interpolation, IC3/PDR and Abstract Interpretation; and we compare the performance 
of verification tools from the Software Verification Competition (SV-COMP'16) and 
Hardware Model Checking Competition (HWMCC'16) that use these techniques.  
%Our benchmarks are drawn from real world hardware benchmark suite, such as 
%VIS verilog models, the Texas-97 Benchmark suite, Hardware Model Checking 
%Competition 2015, and opencores.org.  
	
Though software verifiers are never optimized for RTL verification, 
experimental evaluation on a range of benchmarks suggests that the 
software verification techniques can be successfully used for bounded 
and unbounded RTL verification. The runtimes of SAT/SMT-based software 
verification tools are within one order of magnitude compared to the 
bit-level hardware model checkers.  However, the runtimes of 
abstraction-based techniques, such as abstract interpretation and 
automata-theoretic verification, though operate on an overapproximate 
representation and hence less precise, are comparable to bit-level 
harware tools.  To the best of our knowledge, this is the first 
exhaustive analysis of the state-of-the-art verification techniques 
employed by verification tools from hardware and software domains 
(HWMCC'16 and SV-COMP'16) for the purposes of RTL verification. 
\end{abstract}

\begin{IEEEkeywords}
Formal verification, Verilog RTL, SAT, SMT.
\end{IEEEkeywords}

% ---------------------------------------------------------------------
% Start of text.
% ---------------------------------------------------------------------

%Surely we will cite this~\cite{Clarke:TCA:2004}.

\input{intro}    % Motivation, vision, and contributions
\input{related_work}
\input{contribution}
\input{problem_statement}
\input{abstraction}
\input{v2c}      % The v2c tool
\input{methodology}
\input{equivalence} % Equivalence of Hardware and Software
\input{experiment}    % Conclusions
\input{concl}    % Conclusions

% ---------------------------------------------------------------------
% Un-numbered section of acknowledgments
% ---------------------------------------------------------------------

\section*{Acknowledgments}

% ---------------------------------------------------------------------
% Bibliography
% ---------------------------------------------------------------------

\bibliographystyle{IEEEtran}
\bibliography{biblio}

% ---------------------------------------------------------------------
% Biographies of authors.
% ---------------------------------------------------------------------

% \begin{IEEEbiography}{Rajdeep Mukherjee}
% \end{IEEEbiography}

% \begin{IEEEbiography}{Peter Schrammel}
% \end{IEEEbiography}

% \begin{IEEEbiography}{Tom Melham}
% \end{IEEEbiography}

% \begin{IEEEbiography}{Daniel Kroening}
% \end{IEEEbiography}

% \begin{IEEEbiography}{Michael Tautschnig}
% \end{IEEEbiography}

\end{document}


